A Data-Driven Framework for Neural Field Modeling

### 2011-01-06 ltx/first_order_framework/LaTeX_Manuscript.tex
some minor edits to the relationship to galerkin

Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model. Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get 

@@

The Galerkin projection finds $\mathbf{x}_t$ such that for all basis functions, the inner product with the residual satisfies

@@

	G_i = \int_{\Omega}\Xi(x_t,v_t(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,

@@

The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}. Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where

>>>>

Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model. Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get the approximation of the dynamic field

@@

The Galerkin projection method finds $\mathbf{x}_t$ such that for all of the basis functions the inner product with the residual satisfies

@@

	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0, \> i=0,1,\hdots,n_x-1,

@@

The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}. \dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ become the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
